---
title: "Bike sharing course"
author: "Nannet Fabri"
date: "5-11-2020"
output: word_document
---

## Abstract
I looked for any associations between different parameters and the number of bikes taken per hour. I found an association with the season, the weathertype, the temperature, the 'feels like' temperature, the humidity and the windspeed.

## Material and methods
I looked if there were associations between the number of bikes taken per hour and 8 other parameters during that hour. These were the season, whether or not it was a holiday, whether or not it was a workingday, the weathertype, the temperature, the 'feels like' temperature, the humidity and the windspeed. For the factor variables (season, holiday, workingday and weathertype) I performed a Kruskal Wallis test with a dunn test as post hoc. For the numerical variables (temperature, 'feels like' temperature, humidity and windspeed) I performed a Spearman rank test.

For the above-mentioned tests I first made an R-package, so it was easier to perform them for each pair of variables I wanted to test. I called this R-package 'Bikecourse'.

The package 'Bikecourse', the data and the R-code can be found at my GitHub: https://github.com/NDFabri/Bike_sharing_course

```{r Empty global environment, include=FALSE}
#Empty global environment
rm(list=ls())
```
```{r Install and load packages, include=FALSE}
# Install and load package devtools
if (!requireNamespace("devtools"))
  install.packages("devtools")
library("devtools") #Use of version 2.0.2

# Install and load package Bikecourse
install_github('NDFabri/Bike_sharing_course/packages/Bikecourse@main')
library("Bikecourse") #Use of version 0.1.0

# Install and load package tidyverse
if (!requireNamespace("tidyverse"))
  install.packages("tidyverse")
library("tidyverse") #Use of version 1.2.1

# Install and load package plyr
if (!requireNamespace("plyr"))
  install.packages("plyr")
library("plyr") #Use of version 1.8.4

# Install and load package ggpubr
if (!requireNamespace("ggpubr"))
  install.packages("ggpubr")
library("ggpubr") #Use of version 0.4.0
```
```{r Loading datafile, include=FALSE}
Data <- read_csv("data/train.csv")
```

## Results
```{r Association between count and season, include=FALSE}
#Making season as a factor
Data$season <- as.character(Data$season)

#See if there is an association between count and season
CS <- bikecourse_function(Data$count, Data$season, data=Data,
                    threshold = 0.05,
                    xlab = "season", ylab = "number of bikes",
                    yax = 900, size = 4)
CS #Make a boxplot of the association
```
```{r Association between count and holiday, include=FALSE}
#Making holiday as a factor and renaming values in holiday
Data$holiday <- as.character(Data$holiday)
Data$holiday <- revalue(Data$holiday, c("1"="Yes", "0"="No"))

#See if there is an association between count and holiday
CH <- bikecourse_function(Data$count, Data$holiday, data=Data,
                    threshold = 0.05,
                    xlab = "holiday", ylab = "count",
                    yax = 900, size = 7)
```
```{r Association between count and workingday, include=FALSE}
#Making workingday as a factor and renaming values in workingday
Data$workingday <- as.character(Data$workingday)
Data$workingday <- revalue(Data$workingday, c("1"="Yes", "0"="No"))

#See if there is an association between count and workingday
CW <- bikecourse_function(Data$count, Data$workingday, data=Data,
                    threshold = 0.05,
                    xlab = "workingday", ylab = "count",
                    yax = 900, size = 7)
```
```{r Association between count and weather, include=FALSE}
#Making weather as a factor
Data$weather <- as.character(Data$weather)

#See if there is an association between count and weather
CWe <- bikecourse_function(Data$count, Data$weather, data=Data,
                    threshold = 0.05,
                    xlab = "weathertype", ylab = "",
                    yax = 900, size = 4)
CWe #Make a boxplot of the association
```
```{r Association between count and temp, include=FALSE}
#See if there is an association between count and temp
CT <- bikecourse_function(Data$count, Data$temp, data=Data,
                    threshold = 0.05,
                    xlab = "temperature", ylab = "",
                    yax = 900, size = 7)
CT #Make a scatterplot of the association
```
```{r Association between count and atemp, include=FALSE}
#See if there is an association between count and atemp
CA <- bikecourse_function(Data$count, Data$atemp, data=Data,
                    threshold = 0.05,
                    xlab = "'feels like' temperature", ylab = "number of bikes",
                    yax = 900, size = 7)
CA #Make a scatterplot of the association
```
```{r Association between count and humidity, include=FALSE}
#See if there is an association between count and humidity
CHu <-bikecourse_function(Data$count, Data$humidity, data=Data,
                    threshold = 0.05,
                    xlab = "humidity", ylab = "",
                    yax = 900, size = 7)
CHu #Make a scatterplot of the association
```
```{r Association between count and windspeed, include=FALSE}
#See if there is an association between count and windspeed
CWi <-bikecourse_function(Data$count, Data$windspeed, data=Data,
                    threshold = 0.05,
                    xlab = "windspeed", ylab = "",
                    yax = 900, size = 7)
CWi #Make a scatterplot of the assocation
```
I found an association between the number of bikes taken per hour and the season, the type of weather, the temperature, the 'feels like' temperature, the humidity and the windspeed (Figure 1). I did not find any association between the number of bikes taken per hour and whether or not it is a holiday an whether or not it is a workingday.

```{r Make figure 1, echo=FALSE, fig.height=4.5, fig.width=8.5, message=FALSE}
ggarrange(CS, CWe, CT, CA, CHu, CWi, ncol = 3, nrow = 2)
```

Figure 1: associations between the number of bikes taken per hour (count) and the parameters where I found an association

## Literature
Rstudio version 3.6.0
Database: Fanaee-T, Hadi, and Gama, Joao, Event labeling combining ensemble detectors and background knowledge, Progress in Artificial Intelligence (2013): pp. 1-15, Springer Berlin Heidelberg.